---
title: "Future Learn - Analysis Report"
author: "Nicha Wilanan"
date: "2024-10-31"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir= normalizePath('..'))
```


```{r, include=FALSE, message=FALSE}
library(ProjectTemplate)
load.project()
```

# Introduction
TODO:

# CRISP-DM Round 1

## 1. Business Understandings

## 1.1 Determine Business Objective
This report aims to gather information for an author of self-development books who would like to share valuable tips for people who aspire to do self-learning in their free time. In the world's current trends, there are so many concepts to learn with less time. The stakeholder's objective is to help people achieve their goals by extracting the essence of success factors to finish self-paced learning. The stakeholder aims to dedicate one chapter of the book to tell anecdotes of how some people can finish the online course while others don't as an exemplar for the readers to follow. Therefore, the criteria for the success finding in this report is to find the common characteristics of those who successfully finish the online course, which is unique to the people who do not complete the course.

## 1.2 Assess Situation 
The risk for the report is that it relies mainly on the learner’s survey response, so the answer may not be accurate in case the learners do not answer truthfully. Moreover, the analysis may not reflect all learners’ method of study as there are only minority of learners complete the survey.

There is one terminology in this phase, which is the word *learner archetype*. The learner archetype groups learners with the same behavior together. In this report, there are 7 archetypes - advancers, explorers, fixers, flourishers, hobbyists, preparers and vitalisers. If you want to learn more about each archetype, you can go through this [link.](https://ugc.futurelearn.com/uploads/files/2f/ce/2fce94dd-54e6-4614-972d-ce9c3a6d7d91/Learner-Archetypes.pdf)

## 1.3 Produce Project Plan 
The analysis will follow the CRISP-DM methodologies for two cycles in order to get the key factors leads to course completion. Each cycle will come up with different factors that potentially lead to finish the course. After exploring and analyse data, each factor will be evaluated. In this research, R language is used to extract the insights through statistical summary and visualization. 

Initially, the research question for the first cycle is:

**Do the learner archetypes affect online course success rate?**

## 1.4 Determine Data Mining Goals
If archetype is significant to the MOOC finish rate, there should be a huge difference in the archetype of finisher and those who unable to finish the course. However, if the archetype is quite similar in both groups, it cannot be deduce that the archetype has an effect on the course completion.

# 2. Data Understanding
## 2.1 Collect Initial Data
## 2.2 Describe Data
## 2.3 Explore Data
## 2.4 Verify Data Quality

