---
title: "Impact of learner archetype on study outcome and study method"
author: "Nicha Wilanan"
date: "Semester 1 2024/2025"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir= normalizePath('..'))
```


```{r, include=FALSE, message=FALSE}
library(ProjectTemplate)
load.project()
```

# Introduction
This report analyses the **impact of archetype on study outcome and methodology** to answer the questions of the stakeholder, a researcher studying the learning strategies for each archetype for the best outcome. The online course data and survey are the material used to answer the question of how the learner archetype and the study method can impact the successful outcome of studying online courses. The procedure to construct the research is using two cycles of Cross-Industry Standard Process for Data Mining (CRISP-DM). The first cycle will be conducted to examine whether the archetype has an impact on course completion. Then, the second cycle will built on top of the first cycle, depending on the result. If the result suggests that some archetypes successfully dominate the course completion outcome, the second cycle will focus on the behaviour of those archetypes. On the contrary, if the result shows that the archetypes do not contribute to the success, the behaviour of the learners of each archetype who completed the course will be investigated to show the study pattern to finish the online course by different types of learners.

# CRISP-DM Round 1

## 1. Business Understandings

## 1.1 Determine Business Objective
The first cycle of this report aims to find the impact of the learner archetype on course completion. This question is the main topic of this research that will shape the following cycle's question. By getting to know whether or not the archetype affects learners' completion rate, the stakeholders can have a general idea of what archetype the learners should have to have a higher chance to complete the course. If there is an archetype that completes the course more than others, the researcher may advise learners to approach the study material with that particular mindset. On the other hand, if the archetype is not a significant factor in course completion, each archetype has a fair chance of completing the course, and it will be investigated further in the next cycle on the study pattern of the archetype.

## 1.2 Assess Situation 
The risk for the report is that it relies mainly on the learner’s survey response on their archetype, so the answer may not be accurate in case the learners do not answer truthfully. Moreover, the analysis may not reflect all learners’ method of study as there are only a minority of learners complete the survey. 

There is one terminology in this phase, which is the word *learner archetype*. The archetype is the goal and mindset that the learners have when approaching the study. It groups learners with the same goal together. In this report, there are 7 archetypes - advancers, explorers, fixers, flourishers, hobbyists, preparers and vitalisers. To learn more about the archetype, go through this  [link.](https://ugc.futurelearn.com/uploads/files/2f/ce/2fce94dd-54e6-4614-972d-ce9c3a6d7d91/Learner-Archetypes.pdf)

## 1.3 Determine Data Mining Goals
To know that the learners' archetype affect online course completion rate, a solid pattern of completion for the archetype on every run must be found. If the completion rate in each archetypes are random, it cannot be deduce that the archetype actually affect the course completion.

Initially, the research question will aim to see the result of the course completion on each archetype. The main research topic for this cycle is: 

**Does the learner archetype affect online course completion rate?** 

Noted that the *completion* in this report refers to the learners who accomplished more than 80% of the course content.

## 1.4 Produce Project Plan 
After come up with a main research topic, the data is going to be cleaned, explored and analysed. Then, the findings will be evaluated. In this research, R language is used to extract the insights through statistical summary and visualization.  


## 2. Data Understanding
## 2.1 Collect Initial Data
Future-Learn collected and provided the data that will be used in this report. For this CRISP-DM cycle, three groups of datasets will be utilized. First is the data of archetype survey responses, which will be used to gather the learner's archetype. Second is the course enrollment data that tells how many people enrolled in each course. Lastly, the course activity determines how far the learner goes through the steps in the course.

## 2.2 Describe Data

The data is gathered from a course named **Cyber Security: Safety at Home, Online, in Life.** This course is designed to be finished in three weeks. Each week consists of multiple steps, including articles, videos, quizzes, and discussions. From September 2016 to September 2018, the course had been run for 7 times. Throughout the years, steps are added to enhance learner understandings. From `r count(distinct(activity_1, week_number, step_number))` steps in the first run, the run was gradually enhanced to `r count(distinct(activity_7, week_number, step_number))` steps in the seventh run. The datasets of archetype, course enrollment, and course activity are kept for each run.

These are the list of tables for this analysis and its field name:

1. Enrollment: `r colnames(cyber.security.1_enrolments)`
2. Activity Step: `r colnames(cyber.security.1_step.activity)`
3. Archetype Survey Response: `r colnames(cyber.security.3_archetype.survey.responses)`

The field that are picked for the analysis will be mentioned in part 3.1.


## 2.3 Explore Data

```{r, echo=FALSE}
# Get the enrollment number for each run
enroll_num <- c(
    nrow(unique(enroll_1[, 'learner_id'])),
    nrow(unique(enroll_2[, 'learner_id'])),
    nrow(unique(enroll_3[, 'learner_id'])),
    nrow(unique(enroll_4[, 'learner_id'])),
    nrow(unique(enroll_5[, 'learner_id'])),
    nrow(unique(enroll_6[, 'learner_id'])),
    nrow(unique(enroll_7[, 'learner_id']))
)

# Add comma to the enrollment number 
enroll_num_prettify <- formatC(enroll_num,format="d", big.mark=",")

# Get the number of learner who complete the course in each run
finish_num <- c(
    nrow(activity_1_learner_progress_archetype |> filter(finish_percentage > 80)),
    nrow(activity_2_learner_progress_archetype |> filter(finish_percentage > 80)),
    nrow(activity_3_learner_progress_archetype |> filter(finish_percentage > 80)),
    nrow(activity_4_learner_progress_archetype |> filter(finish_percentage > 80)),
    nrow(activity_5_learner_progress_archetype |> filter(finish_percentage > 80)),
    nrow(activity_6_learner_progress_archetype |> filter(finish_percentage > 80)),
    nrow(activity_7_learner_progress_archetype |> filter(finish_percentage > 80))
)

# Add comma to the course completion number
finish_num_prettify <- formatC(finish_num,format="d", big.mark=",")

# Calculate the percentage of course completion
percent_finish <- paste(round(finish_num/enroll_num * 100, 2), "%")

# Construct the enrollment and completion data frame
enroll_and_finish_df <- data.frame(Enrollment=enroll_num_prettify, Finisher=finish_num_prettify, Finisher_Percentage = percent_finish)

# Add row name
rownames(enroll_and_finish_df) <- c('Run 1', 'Run 2', 'Run 3', 'Run 4', 'Run 5', 'Run 6', 'Run 7')

# Show the result as a table
kable(enroll_and_finish_df, caption = "Enrollment and course finisher percentage")
```

The table above shows a vast difference in the enrollment number and the finisher in each run. In this report, the learners are considered to finish the course if they finish more than or equal to 80% of the activities. There is a clear pattern that most people do not finish the course, with the lowest number of finishers compared to the enroller in Run 6 at approximately 10% and the highest number in Run 5 at almost 20%. 

```{r, echo=FALSE, out.width="70%", fig.align='center', fig.cap="Number of learners by archetype in each run"}
# Construct the theme for subplot
common_theme <- theme_minimal() +
    theme(
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        legend.position="none", # Remove individual legends
    )

# Construct the color value representing each archetype for subplot
common_scale <- scale_fill_manual(
    name = "Archetype",
    values = c(
        "Advancers" = "#F08080",
        "Explorers" = "#DAA520",
        "Fixers" = "#90EE90",
        "Flourishers" = "#98FB98",
        "Hobbyists" = "#40E0D0",
        "Other" = "#87CEEB",
        "Preparers" = "#DDA0DD",
        "Vitalisers" = "#FF69B4"
    )
)

# Plot a graph of counting number of learners in each archetype for run 3
a_3 <- archetype_counts |> filter(run=="3") |> 
    ggplot(aes(x = archetype, y = count, fill = archetype)) + 
    geom_bar(stat='identity') +
    common_theme +
    common_scale +
    labs(
        x = "Archetype",
        y = "Count",
        title = "Run 3"
    )

# Plot a graph of counting number of learners in each archetype for run 4
a_4 <- archetype_counts |> filter(run=="4") |> 
    ggplot(aes(x = archetype, y = count, fill = archetype)) + 
    geom_bar(stat='identity') +
    common_theme +
    common_scale +
    labs(
        x = "Archetype",
        y = "Count",
        title = "Run 4"
    )

# Plot a graph of counting number of learners in each archetype for run 5
a_5 <- archetype_counts |> filter(run=="5") |> 
    ggplot(aes(x = archetype, y = count, fill = archetype)) + 
    geom_bar(stat='identity') +
    common_theme +
    common_scale +
    labs(
        x = "Archetype",
        y = "Count",
        title = "Run 5"
    )

# Plot a graph of counting number of learners in each archetype for run 6
a_6 <- archetype_counts |> filter(run=="6") |> 
    ggplot(aes(x = archetype, y = count, fill = archetype)) + 
    geom_bar(stat='identity') +
    common_theme +
    common_scale +
    labs(
        x = "Archetype",
        y = "Count",
        title = "Run 6"
    )

# Plot a graph of counting number of learners in each archetype for run 7
a_7 <- archetype_counts |> 
    filter(run=="7") |> 
    ggplot(aes(x = archetype, y = count, fill = archetype)) +
    common_theme +
    geom_bar(stat='identity') +
    common_scale +
    labs(
        x = "Archetype",
        y = "Count",
        title = "Run 7"
    )

# Aggregate the archetype count subplot together
archetype_plot <- ggarrange(a_3, a_4, a_5, a_6, a_7,  common.legend = TRUE, legend = "bottom")

# Annotate the plot to show and add title to the plot
annotate_figure(
  archetype_plot, 
  top = text_grob(
          "Number of learners by archetype in each run", 
          face = "bold", 
          size = 12, 
          hjust = 0, 
          vjust = 0.4, 
          x = 0
  )
)
```


When comparing the number of archetype in each run, it is obvious that the number of each archetype does not distribute evenly among the learners. The top 4 archetypes posess by the learner are *Vitalisers*, *Advancers*, *Explorers* and *Fixers*.


## 2.4 Verify Data Quality

The data quality of this round analysis is quite good and there are no missing data in the available table. Although archetype survey response of Run 1 and Run 2 were not kept, the report can still analyse the link between archetype and learner finishing rate from other runs. The only concern is that the survey response rate is low comparing to the enrollment, which will be hard to deduce the result of archetype effect from a whole enrollment population.

```{r, echo=FALSE}
# Count the number of archetype survey response for each run
archetype_response_num <- c(
    nrow(arch_1),
    nrow(arch_2),
    nrow(arch_3),
    nrow(arch_4),
    nrow(arch_5),
    nrow(arch_6),
    nrow(arch_7)
)

# Calculate the percentage of survey response compare to all enrolment number
percent_response <- paste(round(archetype_response_num/enroll_num * 100, 2), "%")

# Construct the enrollment and survey response data frame
enroll_and_response_df <- data.frame(Enrollment=enroll_num_prettify, Response_Survey=archetype_response_num, Response_Percentage = percent_response)

# Add row names
rownames(enroll_and_response_df) <- c('Run 1', 'Run 2', 'Run 3', 'Run 4', 'Run 5', 'Run 6', 'Run 7')

# Show the result table
kable(enroll_and_response_df, caption="Archetype response survey percentage")
```

## 3. Data Preparation
## 3.1 Select Data

1. Enrolment:
The enrolment data is used just for the exploratory purpose and to understand learners more. There is no direct use to answer the main questions on the archetype.

2. Activity Step:
This data is going to be used as a criteria on finding successful learner. To check that learners completed more than 80% of the steps in the module, the learner_id, week_number, step_number, and last_completed_at will be used.

3. Archetype:
This table is another main table that will be used along with the activity step. It is needed to know the learner archetype. There are two column being used, learner_id and archetype.


## 3.2 Clean Data
The data selected is quite clean, so we are going to clean it just by select the fields needed and keep only the unique rows.

## 3.3 Construct Data
After selected the field, new table is created from attributes in the activity step data set. This new table calls *learner_progress*, which contains learner progress and the archetype. Each run has its own *learner_progress* table. To construct the new table, firstly, count the number of steps each learner finished. Then, compare number of finished steps to number of all steps and put it in *finish_percentage* field. Later, add *finish* field that stores boolean value of whether the steps are complete more than 80%.

## 3.4 Integrate Data
Afterwards, the *learner_progress* table is merged with the archetype table by *learner_id* to show the type of each learner if any. This new table is called *learner_progress_archetype.* Again, each run has its own *learner_progress_archetype* table.

## 4. Modelling
```{r, echo=FALSE}
# Construct the summary table for run 3 on the number of learners who complete and not complete the course by archetype
a_3_summary <- activity_3_learner_progress_archetype |> 
    group_by(archetype, finish) |> 
    summarize(count = n(), .groups = 'drop') |>
    pivot_wider(names_from = archetype, values_from = count) |>
    mutate(Run = "3") |>
    mutate(Preparers = 0) |>
    relocate(Run, .after = finish) |>
    relocate(Preparers, .after = Other)

# Construct the summary table for run 4 on the number of learners who complete and not complete the course by archetype
a_4_summary <- activity_4_learner_progress_archetype |> 
    group_by(archetype, finish) |> 
    summarize(count = n(), .groups = 'drop') |>
    pivot_wider(names_from = archetype, values_from = count) |>
    mutate(Run = "4") |>
    relocate(Run, .after = finish)

# Construct the summary table for run 5 on the number of learners who complete and not complete the course by archetype
a_5_summary <- activity_5_learner_progress_archetype |> 
    group_by(archetype, finish) |> 
    summarize(count = n(), .groups = 'drop') |>
    pivot_wider(names_from = archetype, values_from = count) |>
    mutate(Run = "5") |>
    relocate(Run, .after = finish)

# Construct the summary table for run 6 on the number of learners who complete and not complete the course by archetype
a_6_summary <- activity_6_learner_progress_archetype |> 
    group_by(archetype, finish) |> 
    summarize(count = n(), .groups = 'drop') |>
    pivot_wider(names_from = archetype, values_from = count) |>
    mutate(Run = "6") |>
    relocate(Run, .after = finish)

# Construct the summary table for run 7 on the number of learners who complete and not complete the course by archetype
a_7_summary <- activity_7_learner_progress_archetype |> 
    group_by(archetype, finish) |> 
    summarize(count = n(), .groups = 'drop') |>
    pivot_wider(names_from = archetype, values_from = count) |>
    mutate(Run = "7") |>
    relocate(Run, .after = finish)

# Construct the summary table for all runs on the number of learners who COMPLETE the course by archetype
complete_learner_archetype <- rbind(
    a_3_summary,
    a_4_summary,
    a_5_summary,
    a_6_summary,
    a_7_summary
) |> filter(finish == TRUE) |> select(-finish)

# Use zero for the archetype with no data
complete_learner_archetype[is.na(complete_learner_archetype)] <- 0

# Construct the summary table for all runs on the number of learners who NOT COMPLETE the course by archetype
incomplete_learner_archetype <- rbind(
    a_3_summary,
    a_4_summary,
    a_5_summary,
    a_6_summary,
    a_7_summary
) |> filter(finish == FALSE) |> select(-finish)

# Use zero for the archetype with no data 
incomplete_learner_archetype[is.na(incomplete_learner_archetype)] <- 0
```


As right now we have all data prepared, we will examine our main research topic for this round, **Does the learner archetype affect online course completion rate?**

## 4.1 Archetype of learners who completed the course
Let start by take a look at the table below on the archetype of the learner who complete the course.

```{r, echo=FALSE}
kable(complete_learner_archetype, caption = "Archetype of the learners who complete the course")
```

As mentioned before, not many people response to the survey of the archetype, so the majority of learner archetype is unknown. If we ignore unknown type, depends on each run, some archetype perform better than the others. To compare fairly, the data is scaled for each run, so that the number of completers can be compare properly throughout different run. Or else the priority would be given to the run with higher enrollment as higher enrolment has higher chance to have a higher finishers. The brighter color on the heatmap represents more number of successful learners in that archetype.


```{r, echo=FALSE, out.width="70%", fig.align='center', fig.cap="Heatmap showing scaled number of learners who complete the course in each run"}
# Filter archetype and scale the data by row
scale_complete <- subset(complete_learner_archetype, select=-c(Run, Other, `NA`)) |>
    apply(1, scale) |> as.data.frame()

# Add column name
colnames(scale_complete) <- c('Run 3', 'Run 4', 'Run 5', 'Run 6', 'Run 7')

# Add row name
rownames(scale_complete) <- c('Advancers', 'Explorers', 'Fixers', 'Flourishers', 'Hobbyists', 'Preparers', 'Vitalisers')

# Update the row name to column archetype
scale_complete <- tibble::rownames_to_column(scale_complete, "archetype")

# Prepare heatmap data by pivot longer
heatmap_data <- scale_complete |>
    pivot_longer(cols = starts_with("Run"),
                names_to = "Run",
                values_to = "Scale")

# Plot the heatmap comparing the scale of learner who completed the course
scale_completion_plot <- ggplot(heatmap_data, aes(x = Run, y = archetype, fill = Scale)) +
    geom_tile() +
    scale_fill_viridis_c(option = "A") +
    theme_minimal() +
    labs(x = "run")

# Annotate figure
annotate_figure(
  scale_completion_plot, 
  top = text_grob(
          "Heatmap showing scaled number of learners who complete the course in each run", 
          face = "bold", 
          size = 12, 
          hjust = 0, 
          vjust = 0.4, 
          x = 0
  )
)
```


From the heatmap, it is evident that *vitalisers* archetype perform best in all run comparing to other archetype followed by *advancers* and *explorers*, where they have less completer than the others in some runs. However, it needs to be tackle that did vitalisers perform better just because most people are *vitalisers* or it is really affect the course completion. To check the performance, the success rate vs unsuccess rate for each archetype will be compared.

## 4.2 Success rate for each learners' archetype
For this part, let we determine the ratio of learner with same archetype that complete or not complete the course. If the success rate within the archetype is high, it can be deduced that the archetype affect the online course completion.

```{r, echo=FALSE}
# Calculate the percentage of completion rate for each archetype
success_rate_for_learner_archetype <- 
    round((complete_learner_archetype[,c(-1, -ncol(complete_learner_archetype))]/
         (incomplete_learner_archetype[,c(-1, -ncol(complete_learner_archetype))]+
              complete_learner_archetype[,c(-1, -ncol(complete_learner_archetype))])) * 100, 2)

# Use zero for data that has no value
success_rate_for_learner_archetype[is.na(success_rate_for_learner_archetype)] <- 0 

# Add percentage symbol
success_rate_for_learner_archetype[] <- lapply(success_rate_for_learner_archetype, function(x) paste(format(x, nsmall=2), "%"))

# Remove other archetype
success_rate_for_learner_archetype <- subset(success_rate_for_learner_archetype, select=-c(Other))

# Add field run
success_rate_for_learner_archetype$Run <- c('3', '4', '5', '6', '7')

# Relocate field run to be the first column
success_rate_for_learner_archetype <- success_rate_for_learner_archetype |> relocate(Run, .before = Advancers)

```

```{r, echo=FALSE}
# Show table
kable(success_rate_for_learner_archetype, caption = "Course completion rate by archetype")
```

By checking the percentage of completion on each archetype, the result is low and random among different learner's type in each run. Although the *flourishers* archetype has high completion rate in run 3,4 and 7, the rate is low in the other two. The low success rate among each archetype is not surprising because the overall finish rate as a whole shows in *Table 1* is also low.


## 5. Evaluation
## 5.1 Evaluate Results
After explore the data on archetype and course completion rate thoroughly, the archetype has no distinctive effect on the completion. At first glance, some archetype is standing out to have more number of complete learner but actually that is happening because there are more learner in that archetype as a whole so there is a higher chance for learners in that archetype to finish the course more. When comparing the success rate for each archetype, the result is too random in all archetype to have a significant impact on the course completion. Although the rate of completion of the learner with known archetype is more than the overall completion rate, there is a lack of solid pattern among the archetype in each run. Based on the findings, the archetype does not affect whether or not learner finish the online course.

## 5.2 Review Process
Data wrangling and data exploration have been revisited. The results provided above are legit.

## 5.3 Determine next steps
As the archetype is not the factor of course completion, the stakeholders would like to know further on the strategy that each archetype uses to finish the online course successfully. For the next phase, the research will investigate the study pattern that can lead to success in online course completion for each archetype.

# CRISP-DM Round 2
## 1. Business Understanding
In this round, we are going to investigate the user success rate through users' actions in the course and compare it with archetype.

## 1.1 Determine Business Objective
The stakeholder wants to know the learner archetype study pattern contributing to course completion success. As archetypes alone cannot contribute directly to the completion rate, other factors that lead to success among archetypes will be explored further.

## 1.2 Assess Situation
In this phase, the primary data still rely on the user survey response, which is limited, and the archetype distribution is not symmetrical, so the result may not represent the entire archetype population perfectly. As new data is needed to see the action of each learner archetype, new data is added to this scope to calculate the time it takes for each learner to finish the weekly module of the course. This report will assume that the data were collected accurately and can be used straight away.


## 1.3 Determine Data Mining Goals
The action made by the learners when studying the online courses must be explored to see the pattern that the successful learner with different archetype have. The action chosen to be determined is the time spent to finish a week material of the online course. As the only way to complete the whole online course is to finish each small steps, seeing how long the learner spent to finish each weekly module is a good start to know the characteristics of learner archetype approach to finish the online material.

Therefore, the main research topic for the second cycle is:
**Does the successful learner in each archetype have a unique pattern in time spent on learning weekly material?**


## 1.4 Produce Project Plan
The project plan is similar to the previous phase. The data will be cleaned, explored, analysed, and evaluated using R language. The insights are gained through statistical summary and visualisation.

## 2. Data Understanding
Two datasets as the previous cycle are used, the archetype survey responses and course step activity. However, the detail of data used in step activity will be different as it will be looked in a new question with a new perspective. 

## 2.1 Explore data
In this phase, let's explore the time to complete sub module without taking a look at the archetype yet. The activity step table has columns *first_visited_at* and *last_completed_at* for each steps in the course. When grouping the week number and learner id together, the duration that each learner take to complete the weekly module in each course can be calculated. The *Figure 3* below calculated the duration in days that the successful learner, the learner with more than 80% course completion rate, took to complete the weekly material in run 3 to 7. Run 1 and 2 are ignore because they don't have survey response on archetype that will be used to analyse later on.

Ignoring the outlier from the plot, *Figure 3* shows the trend that most learner that complete the course finished the weekly module within a week. Additionally, most people spend less time as the week module number progress, meaning that the week 3 module is complted faster than the week 1. This exploration is promising in a way that it shows the pattern that genrally finishing the course within the online course recommended time-frame can boost the online course completion rate.

```{r, echo=FALSE, out.width="70%", fig.align='center', fig.cap="Box plot shows duration the learner spend to learn each weekly module of the course"}
# Plot the duration spend to learn each weekly module
boxplot_weekly_module_plot <- weekly_module_time_spent_with_arch |>
    ggplot() + 
    geom_boxplot(aes(x=week_number, y=duration_in_days_int), outliers = FALSE) +
    labs(x = "week module no.", y = "duration in days")

# Annotate figure
annotate_figure(
  boxplot_weekly_module_plot, 
  top = text_grob(
          "Box plot shows duration the learner spend to learn each weekly module", 
          face = "bold", 
          size = 12, 
          hjust = 0, 
          vjust = 0.4, 
          x = 0
  )
)
```


## 2.2 Verify data quality
When going through the data, there are many rows that have too low time to complete the weekly course. For example, the data in the table 5 shows that the learner only take 1 minute or less to complete each step. With this small amount of time, the learner may just skim through the course without finishing it, which is not shows the real complete date like the table claims to. However, there is no method to distinguish that the learner complete the course or just skim through the course, so this report will proceed with the data given.
```{r, include=FALSE}
# Filter data that has too low duration
weekly_module_time_spent_with_arch |> filter(duration_in_days_int < 0.005)

# Check the learner id with low duration
duration_too_low <- cyber.security.3_step.activity |> 
    filter(learner_id == "0ddd3caa-1dde-4679-919e-bfb3c63da321" & week_number == 1) |>
    select(step, step_number, first_visited_at, last_completed_at)
```


```{r, echo=FALSE}
# Show the result as a table
kable(duration_too_low[1:3,], caption = "Lower than usual duration to finish the course")
```

# 3. Data Preparation
## 3.1 Select data
The CRISP-DM cycle 2 is built on top of the cycle 1, so some data in the first cycle will be used in this round too.
These are the list of tables for this cycle:

1. Activity step: This data will be used to find the duration the learner take to complete each weekly module. The fields that will be used are *learner_id*, *week_number*, *first_visited_at*, and *last_completed_at*.
2. Learner progress archetype: The data that have been constructed in the previous round will be utilized as it already contains the field *finish* that indicates whether the learner complete the course, along with the field *archetype* that tells the learner type.

## 3.2 Clean data
This report believed that the data provided by the Future-Learn is cleaned and valid. The process to clean data in this round is to filter out the data that is not valid for usage, such as the data that have no *last_completed_at*. Also, only successful learner will be modeled to see the time the complete learner take, so the data will only filter to have the learner with *finish* = True. The filter out learner by completion status will be done later after the data has been merged with table *Learner progress archetype* by *learner_id* for finish column.

## 3.3 Construct data
After select and filter out the rows, the duration in days is calculate by grouping the learner_id and week_number then find the the *first_visited_at* of that entire week subtract with the last date for *last_completed_at* in the same week. This new table is called *weekly_module_time_spent_for_finisher*. This steps is done on the data of run 3 to 7.

## 3.4 Integrate data
Then, the 5 new tables *weekly_module_time_spent_with_arch* for run 3 to 7, are formed by merging *learner progress archetype* to the *weekly_module_time_spent_for_finisher* to get the learner archetype. Lastly, the 5 tables are combined by row to form the big table that contains *learner_id*, *week_number*, *duration_in_days*, and *archetype.* of all 5 runs together.

## 4. Modelling
With all data prepare ready, the duration graph for each archetype is ready to plot.

```{r, echo=FALSE, out.width="70%", fig.align='center', fig.cap="The duration it takes the successful learner to complete weekly module by archetype"}
# Plot the duration it takes the successful learner to complete weekly module by archetype
duration_each_archetype_plot <- weekly_module_time_spent_with_arch |>
    filter(archetype != '<NA>' & archetype != 'Other') |>
    ggplot() + 
    geom_boxplot(aes(x=week_number, y=duration_in_days_int)) +
    facet_grid(. ~ archetype) + 
    labs(title="The duration it takes the successful learner to complete weekly module by archetype", x ="week module no.", y = "duration in days")

# Annotate figure
annotate_figure(
  duration_each_archetype_plot, 
  top = text_grob(
          "Box plot shows duration the learner spend to learn each weekly module", 
          face = "bold", 
          size = 12, 
          hjust = 0, 
          vjust = 0.4, 
          x = 0
  )
)
```

Based on the plot in the figure 4, each archetype has a distinct number of duration to finish the weekly module. Mostly, learner from all archetype take less than 10 days to complete the weekly material. Three archetypes that take less time to study are *flourishers*, *preparers*, *fixers* in which they most people took less than 10 days to complete a weekly module. On the contrary, other archetype that have not been mentioned have more variability in the time learners took to complete the module. For example, some of the *explorers* may use a day or few to complete the course, but there are some people that took a month to complete the course too.

For the trend that learner spend less time as the week module number progress that we have explored in the *Figure 3*, this trend is still valid in most of the archetype but not for the *vitalisers* and *fixers* where the learner tend to spend the same amount of time for each weekly module.

## 5. Evaluation
That concludes the analysis for cycle 2 of the impact of archetype on the time spent on the weekly material. The box plot in *Figure 4* shows that each archetype has its study methodology for the time spent studying the weekly module. The pattern we see can be linked with the definition and characteristics of the learner type. Such as, *fixers* learn to manage the current aspects of their life, so learners of this type tend to finish the course fast. Also, the *vitalisers*, who learn as a hobby and for the love of learning can finish the course quickly and without a rush toward the end. On the contrary, the *explorers* who learn to decide on what to do next tend to take longer to finish a course and rush to finish the course towards the end.

The model and exploratory analysis in this cycle can answer the business objective of the impact of archetypes on the study methods. The graph shown in *Figure 4* is self-explanatory on how the behaviour of learners in each archetype varies.


## 6. Deployment
The first and second cycles of the CRISP-DM can help answer the questions on the impact of the archetype on the study outcome and study method. For the deployment phase, the report and presentation will be delivered to the stakeholders to understand the findings that have been done in this report analysis.

The presentation will include a recap of the business understanding, the data usage and the graphical representation that shows the insight behind the data provided. Lastly, it will end with a summary that will leave users with the key takeaway of the analysis so that the stakeholders can use it to work on their research on learning strategies for the archetype.